Tight Generalization Bounds for Hard Parameter Sharing in High-dimensional Linear Regression

### 2020-10-12 arxiv/intro.tex
edit section 1.2 and abstract

\begin{abstract}
	Hard parameter sharing is a widely used approach to learn jointly from multiple tasks in many applications, such as text classification. The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making prediction. It becomes increasingly important to understand when they work well on typical data. For example, the performance of hard parameter sharing depends on dataset properties such as their sample sizes. Yet, rigorously formulating such intuition can be challenging.

	This paper analyzes hard parameter sharing in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio. We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample sizes and covariance matrices. We also demonstrate that these estimates for the empirical loss are incredibly accurate in modest dimensions. Finally, our results provide new explainanations to several intriguing empirical phenomena. For example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias. This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
\end{abstract}

>>>>

\begin{abstract}
	Hard parameter sharing is a widely used approach to learn jointly from multiple tasks in many applications, such as text classification. The idea is to use a shared feature space for all tasks, while each task also has a separate layer for making prediction.
%	It becomes increasingly important to understand when they work well on typical data. For example, the performance of hard parameter sharing depends on dataset properties such as their sample sizes. Yet, rigorously formulating such intuition can be challenging.

	This paper studies a fundamental question: How does hard parameter sharing work in high-dimensional linear regression, where the sample size and feature dimension become increasingly large in a fixed ratio? We present tight generalization bounds for two canonical cases: (i) multiple tasks with the same feature covariates; (ii) two tasks with arbitrarily different sample sizes and covariance matrices. We also demonstrate that these estimates for the empirical loss are incredibly accurate in modest dimensions. Finally, our results provide new explainanations to several intriguing empirical phenomena. For example, increasing one task's sample size helps another task initially by reducing variance, but hurts eventually due to increasing bias. This suggests progressively adding data for optimizing hard parameter sharing, and we validate its efficiency in text classification tasks.
\end{abstract}

### 2020-10-12 arxiv/setup.tex
edit section 1.2 and abstract

There is a large body of both classical and recent work on multi-task learning.
We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,R17,ZY17,V20}.
The early work of \citet{B00,BS03,M06} have sought a study of multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
An influential paper by \citet{BBCK10} provides uniform convergence bounds that combines multiple datasets in certain settings.
One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, e.g. \citet{B00,MPR16}.
To the best of our knowledge, we are not aware of any previous work that provide explicit generalization bounds under different sample sizes and covariate shifts.

Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, which is a recent development in the random matrix theory literature.
\citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
This result is later extended to non-identity covariance \cite{Anisotropic} and separable covariance matrices \cite{yang2019spiked}.
%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
These techniques provide the most sharp convergence rates for the asymptotic limit compared to other techniques such as free probability \cite{nica2006lectures}.
To the best of my knowledge, we are not aware of any previous result for the sum of two sample covariance matrices with arbitrary covariance matrices.

>>>>

There is a large body of both classical and recent work on multi-task learning.
We focus our discussion on theoretical works, and refer interested readers to several excellent surveys for general references \cite{PY09,R17,ZY17,V20}.
The early work of \citet{B00,BS03,M06} have sought a study of multi-task learning from a theoretical perspective, often using uniform convergence or Rademacher complexity based techniques.
An influential paper by \citet{BBCK10} provides uniform convergence bounds that combines multiple datasets in certain settings.
One limitation of uniform convergence based techniques is that the results often assume that all  tasks have the same sample size, e.g. \citet{B00,MPR16}.
Secondly, these techniques do not apply to the high-dimensional setting, because the results usually require a sample size at least $p \log p$.

Our proof techniques use the so-called local law of random matrices \cite{erdos2017dynamical}, which is a recent development in the random matrix theory literature.
\citet{isotropic} first proved such a local law for sample covariance matrices with isotropic covariance.
This result is later extended to non-identity covariance \cite{Anisotropic} and separable covariance matrices \cite{yang2019spiked}.
%On the other hand, one may derive the asymptotic result in Theorem \ref{thm_main_RMT} with error $\oo(1)$ using the free addition of two independent random matrices in  theory .
These techniques provide the most sharp convergence rates for the asymptotic limit compared to other techniques such as free probability \cite{nica2006lectures}.
To the best of my knowledge, we are not aware of any previous result for the sum of two sample covariance matrices with arbitrary covariate shifts.
